First Order Alternation

### 2018-11-16 quantifiers/body.tex
ok

As applications of first order alternating automata, we identified
several undecidable problems for which no semi-algorithmic methods
exist: inclusion between recognizable timed languages
\cite{AlurDill94}, languages recognized by finite-memory automata
\cite{KaminskiFrancez94} and emptiness of predicate automata, a model
of first-order alternating automata used to check safety and liveness
properties of parameterized concurrent programs
\cite{Farzan15,Farzan16}.

>>>>

As applications of first order alternating automata, we identified
several undecidable problems for which no semi-algorithmic methods
exist: inclusion between recognizable timed languages
\cite{AlurDill94}, languages recognized by finite-memory automata
\cite{KaminskiFrancez94} and emptiness of predicate automata, a
subclass of first-order alternating automata used to check safety and
liveness properties of parameterized concurrent programs
\cite{Farzan15,Farzan16}.
